\texttt{ensmallen}: a flexible C++ library for efficient function optimization

### 2018-10-16 doc/mlsys_paper/paper.tex
slightly shrink the feature comparison table; fix horizontal line
even more compact acknowledgements
fix: arma::rowvec -> arma::vec

@@

        \cmidrule{2-9}
  \hline

@@

@@

\vspace*{-0.5em}
\begin{minted}[fontsize=\small]{c++}
    double EvaluateWithGradient(const arma::mat& theta, arma::mat& gradient) {
      const arma::rowvec v = (y - X * theta); // Cache result
      gradient = -2 * X.t() * v;  // Store gradient in the provided matrix
      return arma::accu(v % v); // Take squared norm of v
    }
\end{minted}
\vspace*{-0.5em}

@@

\subsubsection*{Acknowledgements}
\vspace*{-0.5em}

We would like to thank the many contributors to {\tt ensmallen},
who are listed on the associated website.

% The development team of {\tt ensmallen} does not include just the authors named
% here but also a long list of other contributors.  See
% \url{https://www.ensmallen.org/about.html} for more information.
% % TODO: that URL may change

>>>>

\begin{adjustbox}{scale={0.95}{0.95}}

@@

@@

\end{adjustbox}

@@

\vspace*{-0.5em}
\begin{minted}[fontsize=\small]{c++}
    double EvaluateWithGradient(const arma::mat& theta, arma::mat& gradient) {
      const arma::vec v = (y - X * theta); // Cache result
      gradient = -2 * X.t() * v;  // Store gradient in the provided matrix
      return arma::accu(v % v); // Take squared norm of v
    }
\end{minted}
\vspace*{-0.5em}

@@

%\begin{small}
{\bf Acknowledgements.}
We would like to thank the many contributors to {\tt ensmallen},
who are listed on the associated website.
%\end{small}

% \subsubsection*{Acknowledgements}
% \vspace*{-0.5em}
% 
% The development team of {\tt ensmallen} does not include just the authors named
% here but also a long list of other contributors.  See
% \url{https://www.ensmallen.org/about.html} for more information.
% % TODO: that URL may change
